---
title: "visualisation"
author: "MG"
date: "2023-05-03"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
setwd("~/Fac/Master_Rennes/stage1/edges")

library(tidyverse)
library(ggpubr)
library(igraph)
library(RColorBrewer)
source("exploratory_code/functions.R")
```

```{r}
main_theme = theme_bw()+
  theme(line = element_blank(), 
        axis.line = element_line(colour = "black"),
        panel.border = element_blank(),
        axis.ticks =  element_line(colour = "black"),
        axis.text.x = element_text(colour = "black", size=17),
        axis.text.y = element_text(colour = "black", size=17),
        legend.title = element_text(colour = "black", size=17),
        legend.text = element_text(colour = "black", size=15),
        axis.title=element_text(size=15))
```

```{r}
importance_df = read.csv("exploratory_output/importance_df.csv",
                         stringsAsFactors = T)
communicability_df = read.csv("exploratory_output/communicability_df.csv",
                         stringsAsFactors = T)
all_norm_svd = read.csv("exploratory_output/all_norm_svd_subset.csv",
                        stringsAsFactors = T)
communicability_shared_edges_df = read.csv("exploratory_output/communicability_shared_edges_df.csv",
                                           stringsAsFactors = T)
str(importance_df)
str(all_norm_svd)
str(communicability_shared_edges_df)
all_data = importance_df%>%
  left_join(all_norm_svd,by = c("X","virus","host") )%>%
  left_join(communicability_shared_edges_df,by = c("X","virus","host") )
str(all_data)
```
## Check the link between the importance metrique(I) and the communicability (G)
$$G=\sum^n_{j=1}\varphi_j\varphi_j^Te^{\lambda_j}$$
with $\varphi_j = $eigenvector associate with the eigenvalue j

$$I = G - \zeta G$$
$\zetaG$ is the comunicability with a small modification in the ntw (eg. an edge remove)
```{r}
clover_G_I = ggplot(all_data)+
  geom_point(aes(G_clover_share, importance_clover))+
  xlab("Communicability of share edge") + ylab("importance of share edge")+
  main_theme
trefle_G_I = ggplot(all_data)+
  geom_point(aes(G_trefle_share, importance_trefle))+
  xlab("Communicability of share edge") + ylab("importance of share edge")+
  main_theme

ggarrange(clover_G_I,trefle_G_I, labels = c("clover","trefle"),ncol = 2)
```

Normalisation of the dat aare problematic here. On the graphs we are looking at : 
$$I_{pq} = |G_{pq} - \zeta G_{pq}|_1$$
It's fair to supose that most of the time when an edge connecting p-q is remove, the most impacted $\zeta G$ will be $\zeta G_{pq}$. **It will deacrease strongly $\zeta G_{pq}$**.
So, knowing that the perturbation is always done by removing the edge p-q that we observe, most of the time the  $|G - \zeta G|_1$ normalization will have as max  $G_{pq} - \zeta G_{pq}$ **beacause $\zeta G_{pq}$ is small while other $\zeta G_{ij} are big (because less impacted by the remove) **. The result is that the difference will most of the time make the $I_{pq}$ big because  $G_{pq} - \zeta G_{pq} \approx G_{pq}$ when the number of edge connected to q and p are small. So because of this will always over estimate the true importance of the p-q edge with small connection

```{r eval=FALSE, include=FALSE}
I_clover_1 = all_data%>%
  filter(importance_clover==1)%>%
  select(host,virus)
all_data%>%
  filter(host=="Pusa hispida")

I_clover_1 = c(as.character(I_clover_1$virus), 
               as.character(I_clover_1$host))
grh_clover = graph_from_adjacency_matrix(uni_ntw_clover,mode = "undirected")

V(grh_clover)$name[!(V(grh_clover)$name %in% c("Pusa hispida","Phocid alphaherpesvirus 1"))] = NA
plot(grh_clover,edge.arrow.size=.2, vertex.size=1,vertex.label=V(grh_clover)$media,
      vertex.label.cex = .4, vertex.label.color="gray40")
grh_clover = graph_from_adjacency_matrix(uni_ntw_clover,mode = "undirected")
V(grh_clover)$name[!(V(grh_clover)$name %in% I_clover_1)] = NA

plot(grh_clover,edge.arrow.size=.2, vertex.size=1,vertex.label=V(grh_clover)$media,
      vertex.label.cex = 2, vertex.label.color="gray40",
     edge.color=ifelse(cust > 0, "blue","red"))

test = all_data%>%
  select(host,virus,importance_clover)

gg <- graph.data.frame(test,directed=FALSE)

display.brewer.all()

brewer.pal(n=9,name ="YlOrRd" )[4:8]
edge_color = ifelse(test$importance_clover==1, "blue",
              ifelse(test$importance_clover==0, brewer.pal(n=9,name ="YlOrRd" )[3],
               ifelse(test$importance_clover<0.25, brewer.pal(n=9,name ="YlOrRd" )[5],
                ifelse(test$importance_clover<0.75, brewer.pal(n=9,name ="YlOrRd" )[6],
                 brewer.pal(n=9,name ="YlOrRd" )[7])
               )))
               
plot(gg, vertex.size=1,vertex.label=V(grh_clover)$media,
      vertex.label.cex = 2, vertex.label.color="black",edge.width = 8,
     edge.label=round(test$importance_clover,2),edge.label.cex = 2,
     edge.color = edge_color)

```

Conclusion ,the metric "I" don't behave as expected for the isolated species and for the "tip species" = that have only one egde

```{r include=FALSE}
grh_clover = graph_from_adjacency_matrix(uni_ntw_clover,mode = "undirected")
max(all_data$G_trefle_share)
edge_color2 = ifelse(all_data$G_clover_share>=0.75, "blue",
              ifelse(all_data$G_clover_share<0.25, brewer.pal(n=9,name ="YlOrRd" )[3],
               ifelse(all_data$G_clover_share<0.5, brewer.pal(n=9,name ="YlOrRd" )[5],
                ifelse(all_data$G_clover_share<0.75, brewer.pal(n=9,name ="YlOrRd" )[6],
                 brewer.pal(n=9,name ="YlOrRd" )[7])
               )))
plot(grh_clover, vertex.size=1,vertex.label=V(grh_clover)$media,
      vertex.label.cex = 2, vertex.label.color="black",edge.width = 8,
     edge.label=round(all_data$G_trefle_share,2),edge.label.cex = 2,
     edge.color = edge_color2)


```
### Old version of communicability and importance with the bad normalisation explain above
```{r}
head(all_data)
gg_svd_L = ggplot(all_data)+
  geom_point(aes(O_diff_clover_L ,O_diff_trefle_L ))+
  xlab("SVD clover") + ylab("SVD trefle")+
  geom_abline(intercept= 0, slope = 1, "blue")+
  main_theme
gg_svd_R = ggplot(all_data)+
  geom_point(aes(O_diff_clover_R, O_diff_trefle_R))+
  xlab("SVD clover") + ylab("SVD trefle")+
  geom_abline(intercept= 0, slope = 1, "blue")+
  main_theme
gg_G = ggplot(all_data)+
  geom_point(aes( G_clover_share , G_trefle_share ))+
  xlab("communicabilité clover") + ylab("communicabilité trefle")+
  geom_abline(intercept= 0, slope = 1, "blue")+
  main_theme
gg_I = ggplot(all_data)+
  geom_point(aes( importance_clover , importance_trefle))+
  xlab("importance clover") + ylab("importance trefle")+
  geom_abline(intercept= 0, slope = 1, "blue")+
  main_theme
ggarrange(gg_svd_L,gg_svd_R, gg_G, gg_I, labels = c("SVD","SVD","Communicabilité", "Communicabilité diff |G - zeta(G)|"),ncol = 2, nrow = 2)
gg_G = ggplot(all_data)+
  geom_point(aes( G_clover_share , G_trefle_share ))+
  xlab("communicabilité clover") + ylab("communicabilité trefle")+
  geom_abline(intercept= 0, slope = 1, "blue")+
  main_theme
```
### Communicability and importance differente metrics
Communicability_df was produce by the *"communicability_parallel_process.R"* function.
```{r}
str(communicability_df)
str(communicability_df_long)

ggplot(communicability_df)+
  geom_point(aes(normalized(G_pq_clover), normalized(G_pq_trefle)))+
  geom_abline(intercept= 0, slope = 1, col = "blue")+
  main_theme
ggplot(communicability_df)+
  geom_point(aes(G_pq_clover_nrmlz, G_pq_trefle_nrmlz))+
  geom_abline(intercept= 0, slope = 1, col = "blue")+
  main_theme

### Better to look at the importance than the *zeta* communicability when we compare trefle and clover on a scatter plot because the communicability distribution isn't the same in both network resulting in an occultation of the effect the perturbation. Moreover *zeta* communicability is the opposite of the link importance, it is all the noise that we want to get ride of when we do the substration to obtaine I.
ggplot(communicability_df)+
  geom_point(aes(G_pq_zeta_clover_nrmlz, G_pq_zeta_trefle_nrmlz))+
  geom_abline(intercept= 0, slope = 1, col = "blue")+
  main_theme

### zeta G ~ G for colver and trefle, we expect that no point will be above the 1:1 line, this is what we observe so every think seems correct. The points that are far below the line should represent the most importante interactions. 
ggplot(communicability_df)+
  geom_point(aes(G_pq_trefle_nrmlz, G_pq_zeta_trefle_nrmlz))+
  geom_abline(intercept= 0, slope = 1, col = "blue")+
  main_theme
ggplot(communicability_df)+
  geom_point(aes(G_pq_clover_nrmlz, G_pq_zeta_clover_nrmlz))+
  geom_abline(intercept= 0, slope = 1, col = "blue")+
  main_theme

ggplot(communicability_df)+
  geom_point(aes(importance_clover_nrmlz,importance_trefle_nrmlz ))+
  geom_abline(intercept= 0, slope = 1, col = "blue")+
  main_theme
ggplot(communicability_df)+
  geom_point(aes(f_norm_G_clover_nrmlz,f_norm_G_trefle_nrmlz))+
  main_theme
ggplot(communicability_df)+
  geom_point(aes(f_norm_G_clover,f_norm_G_trefle))+
  main_theme
communicability_df[communicability_df$f_norm_G_trefle_nrmlz>0.5,]
```
### Histograme des varaible les plis intersantes
```{r}
str(communicability_df)
G_nrmlz_subset = communicability_df %>%
  select(c(virus, host, X, G_pq_clover_nrmlz, G_pq_trefle_nrmlz))%>%
  pivot_longer(-c(virus, host, X),values_to ="G_nrmlz")

hist_G = ggplot(G_nrmlz_subset)+
  geom_density(aes(G_nrmlz, fill = name),alpha = 0.2, stat = "density")+
  fill_palette("pastel1")+
  main_theme+
  scale_fill_discrete(name = "Network", labels = c("clover", "trefle"))+
  labs(x ="Communicability (G)", y= "Density") 

I_nrmlz_subset = communicability_df %>%
  select(c(virus, host, X, importance_trefle_nrmlz, importance_clover_nrmlz))%>%
  pivot_longer(-c(virus, host, X),values_to ="I_nrmlz")

str(G_nrmlz_subset)

hist_I = ggplot(I_nrmlz_subset)+
  geom_density(aes(I_nrmlz, fill = name),alpha = 0.2, stat = "density")+
  fill_palette("pastel1")+
  scale_fill_discrete(name = "Network", labels = c("clover", "trefle"))+
  labs(x ="Importance", y= "Density") +
  main_theme


gg_G2  = ggplot(communicability_df)+
  geom_point(aes(G_pq_clover_nrmlz, G_pq_trefle_nrmlz))+
  geom_abline(intercept= 0, slope = 1, col = "blue")+
  labs(x ="G colver", y= "G trefle")+
  main_theme

gg_I2 = ggplot(communicability_df)+
  geom_point(aes(importance_clover_nrmlz, importance_trefle_nrmlz))+
  geom_abline(intercept= 0, slope = 1, col = "blue")+
  labs(x ="I colver", y= "I trefle")+
  main_theme
ggarrange(hist_G, hist_I,gg_G2,gg_I2, ncol =2, nrow =2)
```
```{r}
gg_I_F_trefle_nrmlz = ggplot(communicability_df)+
  geom_point(aes(importance_trefle_nrmlz,f_norm_G_trefle_nrmlz ))+
  labs(x ="I trefle", y= "f_norm trefle")+
  main_theme

gg_I_F_clover_nrmlz = ggplot(communicability_df)+
  geom_point(aes(importance_clover_nrmlz,f_norm_G_clover_nrmlz ))+
  labs(x ="I clover", y= "f_norm clover")+
  main_theme
gg_I_F_trefle = ggplot(communicability_df)+
  geom_point(aes(importance_trefle, f_norm_G_trefle ))+
  labs(x ="I trefle", y= "f_norm trefle")+
  main_theme

gg_I_F_clover = ggplot(communicability_df)+
  geom_point(aes(importance_clover, f_norm_G_clover ))+
  labs(x ="I clover", y= "f_norm clover")+
  main_theme
ggplot(communicability_df)+
  geom_point(aes(f_norm_G_clover_nrmlz, f_norm_G_clover ))+
  labs(x ="f_norm clover norm", y= "f_norm clover")+
  main_theme
ggplot(communicability_df)+
  geom_point(aes(f_norm_G_trefle_nrmlz, f_norm_G_trefle ))+
  labs(x ="f_norm clover norm", y= "f_norm clover")+
  main_theme
ggarrange(gg_I_F_trefle, gg_I_F_clover,gg_I_F_trefle_nrmlz, gg_I_F_clover_nrmlz)
communicability_df[communicability_df$importance_trefle == 0 |communicability_df$importance_clover == 0,]
```
The distance between the forbenuis norm of the communicability and the zeta communicability is negatively correlated with the importance metric. It is more continuous and maybe capture in a more efficent way the real impact of the suppretion of the interaction. We can see in the plot I clover~f_ nrom trefle, that there is not gap for the fnorm metric,

### structure of the ntw
#### Communicability and degree of nodes
```{r}
library(lattice)
clover = read.csv("data/clover.csv", stringsAsFactors = T)
trefle = read.csv("data/trefle.csv", stringsAsFactors = T)

##### 1000 interaction for testing /!\to be removed/!\
set.seed(1000)
ID = sample(nrow(clover), 1000)
clover = clover[ID, ]

trefle = trefle[trefle$host %in% clover$Host & trefle$virus %in% clover$Virus ,]
#####

ID_trefle = which( paste(trefle$virus, trefle$host) %in% 
                     paste(clover$Virus, clover$Host))
shared_asso = trefle[ID_trefle, ]


uni_ntw_clover = matrix.associations.uni(Virus = clover$Virus, Host = clover$Host)
uni_ntw_trefle = matrix.associations.uni(Virus = trefle$virus, Host = trefle$host)
G_trefle = communicability(uni_ntw_trefle)
G_clover = communicability(uni_ntw_clover)
names(sort(colSums(uni_ntw_trefle)))
G_trefle_order = G_trefle[names(sort(colSums(uni_ntw_trefle))),
                          names(sort(colSums(uni_ntw_trefle)))]
G_trefle_order_c = G_trefle[names(sort(colSums(uni_ntw_clover))),
                          names(sort(colSums(uni_ntw_clover)))]
G_clover_order = G_clover[names(sort(colSums(uni_ntw_clover))),
                          names(sort(colSums(uni_ntw_clover)))]
# A = matrix(c(0, 1, 0, 1, 0, 1, 0, 1, 1, 0,
#                             1, 0, 0, 1, 0, 1, 1, 0, 1, 1,
#                             0, 0, 0, 0, 0, 0, 1, 1, 0, 0,
#                             1, 1, 0, 0, 0, 0, 1, 1, 1, 1,
#                             0, 0, 0, 0, 0, 1, 1, 0, 1, 1,
#                             1, 1, 0, 0, 1, 0, 1, 0, 0, 0,
#                             0, 1, 1, 1, 1, 1, 0, 0, 1, 1,
#                             1, 0, 1, 1, 0, 0, 0, 0, 0, 0,
#                             1, 1, 0, 1, 1, 0, 1, 0, 0, 1,
#                             0, 1, 0, 1, 1, 0, 1, 0, 1, 0), ncol = 10, nrow =10)
# colnames(A) = c("A", "B"," C", "D", "E", "F", "G", "H", "I", "J")
# rownames(A) = c("A", "B"," C", "D", "E", "F", "G", "H", "I", "J")
# G_A = communicability(A)
# G_A = G_A[names(sort(colSums(A))), names(sort(colSums(A)))]
# levelplot(G_A)
colnames(G_trefle_order) = sort(colSums(uni_ntw_trefle))
rownames(G_trefle_order) = sort(colSums(uni_ntw_trefle))
levelplot(G_trefle_order, 
          scales=list(x=list(at=seq(1, ncol(G_trefle_order), by=10),
                            
                             rot=45), 
                      y=list(at=seq(1, nrow(G_trefle_order), by=10))))



levelplot(G_clover_order)


levelplot(G_trefle_order_c)

```
#### first dim of the communicability

```{r}
spectre_trefle = eigen(uni_ntw_trefle)
spectre_clover = eigen(uni_ntw_trefle)
G1_trefle = spectre_trefle[[2]][1,]%*%t(spectre_trefle[[2]][1,]) * exp(spectre_trefle[[1]][1])
G2_trefle = spectre_trefle[[2]][2,]%*%t(spectre_trefle[[2]][2,]) * exp(spectre_trefle[[1]][1])
G3_trefle = spectre_trefle[[2]][3,]%*%t(spectre_trefle[[2]][3,]) * exp(spectre_trefle[[1]][1])
G4_trefle = spectre_trefle[[2]][4,]%*%t(spectre_trefle[[2]][4,]) * exp(spectre_trefle[[1]][1])
G5_trefle = spectre_trefle[[2]][5,]%*%t(spectre_trefle[[2]][5,]) * exp(spectre_trefle[[1]][1])

dim1 = spectre_trefle[[2]][1,]
dim2 = spectre_trefle[[2]][2,]
dim3 = spectre_trefle[[2]][3,]
dim4 = spectre_trefle[[2]][4,]
dim5 = spectre_trefle[[2]][5,]
names(dim1) = colnames(uni_ntw_trefle)
names(dim2) = colnames(uni_ntw_trefle)
names(dim3) = colnames(uni_ntw_trefle)
names(dim4) = colnames(uni_ntw_trefle)
names(dim5) = colnames(uni_ntw_trefle)

colnames(G1_trefle) = colnames(uni_ntw_trefle)
rownames(G1_trefle) = colnames(uni_ntw_trefle)
colnames(G2_trefle) = colnames(uni_ntw_trefle)
rownames(G2_trefle) = colnames(uni_ntw_trefle)
colnames(G3_trefle) = colnames(uni_ntw_trefle)
rownames(G3_trefle) = colnames(uni_ntw_trefle)
colnames(G4_trefle) = colnames(uni_ntw_trefle)
rownames(G4_trefle) = colnames(uni_ntw_trefle)
colnames(G5_trefle) = colnames(uni_ntw_trefle)
rownames(G5_trefle) = colnames(uni_ntw_trefle)

#G1_trefle_store = G1_trefle[names(sort(colSums(uni_ntw_trefle))),
#                          names(sort(colSums(uni_ntw_trefle)))]

G1_trefle_store = G1_trefle[names(sort(dim1)),
                          names(sort(dim1))]
G2_trefle_store = G2_trefle[names(sort(dim2)),
                          names(sort(dim2))]
G3_trefle_store = G3_trefle[names(sort(dim3)),
                          names(sort(dim3))]
G4_trefle_store = G4_trefle[names(sort(dim4)),
                          names(sort(dim4))]
G5_trefle_store = G5_trefle[names(sort(dim5)),
                          names(sort(dim5))]



p1 = levelplot(G1_trefle_store, scales=list(x=list(at=NULL),y=list(at=NULL)))
p2 = levelplot(G2_trefle_store, scales=list(x=list(at=NULL),y=list(at=NULL)))
p3 = levelplot(G3_trefle_store, scales=list(x=list(at=NULL),y=list(at=NULL)))
p4 = levelplot(G4_trefle_store, scales=list(x=list(at=NULL),y=list(at=NULL)))
p5 = levelplot(G5_trefle_store, scales=list(x=list(at=NULL),y=list(at=NULL)))

ggarrange(p1,p2,p3,p4,p5)
```

```{r include=FALSE}
grh_trefle = graph_from_adjacency_matrix(uni_ntw_trefle,mode = "undirected")
sum(uni_ntw_trefle)/2
max(all_data$G_trefle_share)
str(summary(communicability_df$importance_trefle_nrmlz))
temp = 

ID_share_edges = which(paste(as_edgelist(grh_trefle, names=T)[,1],as_edgelist(grh_trefle, names=T)[,2]) %in% paste(as_edgelist(grh_clover, names=T)[,1],as_edgelist(grh_clover, names=T)[,2]))

I_nomr_trfl = communicability_df$importance_trefle_nrmlz
edge_color_share = ifelse(I_nomr_trfl>=max(I_nomr_trfl) - max(I_nomr_trfl)*0.01 , "blue",
              ifelse(communicability_df$importance_trefle_nrmlz==0, brewer.pal(n=9,name ="YlOrRd" )[2],
               ifelse(I_nomr_trfl<max(I_nomr_trfl) - max(I_nomr_trfl)*0.2, brewer.pal(n=9,name ="YlOrRd" )[6],
                ifelse(I_nomr_trfl<max(I_nomr_trfl) - max(I_nomr_trfl)*0.1, brewer.pal(n=9,name ="YlOrRd" )[7],
                 brewer.pal(n=9,name ="YlOrRd" )[9])
               )))
edge_color_trefle = rep("gray80",length(E(grh_trefle)))
edge_color_trefle[ID_share_edges] <- edge_color_share

edge_width_trefle = rep(8,length(E(grh_trefle)))
edge_width_trefle[-ID_share_edges] =NA
layout.auto()
##### Edges value from trefle
lay = layout.auto(grh_clover)
plot(grh_trefle, vertex.size=1,vertex.label=NA,
      vertex.label.cex = 2,edge.width = edge_width_trefle,
     edge.label=NA,edge.label.cex = 2,
     edge.color = edge_color_trefle)
plot(grh_clover, vertex.size=1,vertex.label=NA,
      vertex.label.cex = 2,edge.width = 8,
     edge.label=NA,edge.label.cex = 2,
     edge.color = edge_color_share, layout = lay)
##### Edges value from clover
I_nomr_clvr = communicability_df$importance_clover_nrmlz
edge_color_share2 = ifelse(I_nomr_clvr>=max(I_nomr_trfl) - max(I_nomr_trfl)*0.01 , "blue",
              ifelse(I_nomr_clvr==0, brewer.pal(n=9,name ="YlOrRd" )[2],
               ifelse(I_nomr_clvr<max(I_nomr_trfl) - max(I_nomr_trfl)*0.2, brewer.pal(n=9,name ="YlOrRd" )[6],
                ifelse(I_nomr_clvr<max(I_nomr_trfl) - max(I_nomr_trfl)*0.1, brewer.pal(n=9,name ="YlOrRd" )[7],
                 brewer.pal(n=9,name ="YlOrRd" )[9])
               )))
plot(grh_clover, vertex.size=1,vertex.label=NA,
      vertex.label.cex = 2,edge.width = 8,
     edge.label=NA,edge.label.cex = 2,
     edge.color = edge_color_share2, layout = lay)
```
