---
title: "visualisation"
author: "MG"
date: "2023-05-03"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
setwd("~/Fac/Master_Rennes/stage1/edges")

library(tidyverse)
library(ggpubr)
library(igraph)
library(RColorBrewer)
```

```{r}
main_theme = theme_bw()+
  theme(line = element_blank(), 
        axis.line = element_line(colour = "black"),
        panel.border = element_blank(),
        axis.ticks =  element_line(colour = "black"),
        axis.text.x = element_text(colour = "black", size=17),
        axis.text.y = element_text(colour = "black", size=17),
        legend.title = element_text(colour = "black", size=17),
        legend.text = element_text(colour = "black", size=15),
        axis.title=element_text(size=15))
```

```{r}
importance_df = read.csv("exploratory_output/importance_df.csv",
                         stringsAsFactors = T)
all_norm_svd = read.csv("exploratory_output/all_norm_svd_subset.csv",
                        stringsAsFactors = T)
communicability_shared_edges_df = read.csv("exploratory_output/communicability_shared_edges_df.csv",
                                           stringsAsFactors = T)
str(importance_df)
str(all_norm_svd)
str(communicability_shared_edges_df)
all_data = importance_df%>%
  left_join(all_norm_svd,by = c("X","virus","host") )%>%
  left_join(communicability_shared_edges_df,by = c("X","virus","host") )
str(all_data)
```
## Check the link between the importance metrique(I) and the communicability (G)
$$G=\sum^n_{j=1}\varphi_j\varphi_j^Te^{\lambda_j}$$
with $\varphi_j = $eigenvector associate with the eigenvalue j

$$I = G - \zeta G$$
$\zetaG$ is the comunicability with a small modification in the ntw (eg. an edge remove)
```{r}
clover_G_I = ggplot(all_data)+
  geom_point(aes(G_clover_share, importance_clover))+
  xlab("Communicability of share edge") + ylab("importance of share edge")+
  main_theme
trefle_G_I = ggplot(all_data)+
  geom_point(aes(G_trefle_share, importance_trefle))+
  xlab("Communicability of share edge") + ylab("importance of share edge")+
  main_theme

ggarrange(clover_G_I,trefle_G_I, labels = c("clover","trefle"),ncol = 2)
```

Normalisation of the dat aare problematic here. On the graphs we are looking at : 
$$I_{pq} = |G_{pq} - \zeta G_{pq}|_1$$
It's fair to supose that most of the time when an edge connecting p-q is remove, the most impacted $\zeta G$ will be $\zeta G_{pq}$. **It will deacrease strongly $\zeta G_{pq}$**.
So, knowing that the perturbation is always done by removing the edge p-q that we observe, most of the time the  $|G - \zeta G|_1$ normalization will have as max  $G_{pq} - \zeta G_{pq}$ **beacause $\zeta G_{pq}$ is small while other $\zeta G_{ij} are big (because less impacted by the remove) **. The result is that the difference will most of the time make the $I_{pq}$ big because  $G_{pq} - \zeta G_{pq} \approx G_{pq}$ when the number of edge connected to q and p are small. So because of this will always over estimate the true importance of the p-q edge with small connection

```{r}
I_clover_1 = all_data%>%
  filter(importance_clover==1)%>%
  select(host,virus)
all_data%>%
  filter(host=="Pusa hispida")

I_clover_1 = c(as.character(I_clover_1$virus), 
               as.character(I_clover_1$host))
grh_clover = graph_from_adjacency_matrix(uni_ntw_clover,mode = "undirected")

V(grh_clover)$name[!(V(grh_clover)$name %in% c("Pusa hispida","Phocid alphaherpesvirus 1"))] = NA
plot(grh_clover,edge.arrow.size=.2, vertex.size=1,vertex.label=V(grh_clover)$media,
      vertex.label.cex = .4, vertex.label.color="gray40")
grh_clover = graph_from_adjacency_matrix(uni_ntw_clover,mode = "undirected")
V(grh_clover)$name[!(V(grh_clover)$name %in% I_clover_1)] = NA

plot(grh_clover,edge.arrow.size=.2, vertex.size=1,vertex.label=V(grh_clover)$media,
      vertex.label.cex = 2, vertex.label.color="gray40",
     edge.color=ifelse(cust > 0, "blue","red"))

test = all_data%>%
  select(host,virus,importance_clover)

gg <- graph.data.frame(test,directed=FALSE)

display.brewer.all()

brewer.pal(n=9,name ="YlOrRd" )[4:8]
edge_color = ifelse(test$importance_clover==1, "blue",
              ifelse(test$importance_clover==0, brewer.pal(n=9,name ="YlOrRd" )[3],
               ifelse(test$importance_clover<0.25, brewer.pal(n=9,name ="YlOrRd" )[5],
                ifelse(test$importance_clover<0.75, brewer.pal(n=9,name ="YlOrRd" )[6],
                 brewer.pal(n=9,name ="YlOrRd" )[7])
               )))
               
plot(gg, vertex.size=1,vertex.label=V(grh_clover)$media,
      vertex.label.cex = 2, vertex.label.color="black",edge.width = 8,
     edge.label=round(test$importance_clover,2),edge.label.cex = 2,
     edge.color = edge_color)

```

Conclusion ,the metric "I" don't behave as expected for the isolated species and for the "tip species" = that have only one egde




